---
title: "Figures for HW"
author: "Yang Liu"
output:
  pdf_document:
    toc: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, message=FALSE, warning=FALSE,
                      fig.width = 6, fig.height = 3.5)

```
  
  
_This documents contains figures for HW showing the convergence of the sequence of functions_  

```{r}
# 2/17/2019
library(ggplot2)
library(data.table)
# the plot function
plot.f <- function(f, 
                   N_range =c(1, 2, 3, 5, 10), # the range of N in Z+
                   xaxis_range = c(0, 10), # the x-axis range
                   y1 = NA, y2 = NA, # the y-axis range
                   n_points = 500) # how many points for each line
  {
  # N in Z+, how many N to show? 
  # N = c(1:5,10,20,100)
  if (any(N_range < 1)) stop("Check N range \n")
  # the x-axis range is default to be between 0, 10, need to change accordingly 
  if (length(xaxis_range)!=2) stop("Check x axis input \n")
  x <- seq(from = xaxis_range[1] , to = xaxis_range[2], length.out = n_points)
  # create a wide table, each N is a column
  df <- as.data.table(cbind(x, sapply(N_range, f, x = x)))
  setnames(df, c("x", paste0("n=",N_range))) 
  df.m1 <- melt(df, measure.vars = paste0("n=",N_range))
  names(df.m1) <- c("x", "n", "y")
  df.m1[, n:=as.factor(n)]
  ggplot(data = df.m1, aes(x=x, y=y, color = n, group = n))  + 
    geom_line(lwd = 0.8) + 
    geom_vline(xintercept = 0, color = 'grey') +
    geom_hline(yintercept = 0, color = 'grey') + 
    theme_classic() + 
    scale_color_brewer(palette="BuPu")+
    # scale_color_grey() +
    labs(y = 'fn(x)') + 
    scale_x_continuous(breaks = c(-10, -5, -1, 0, 1, 5,10))+  # x breaks won't go beyond this range I suppose + 
    scale_y_continuous(limits = c(y1, y2))
}

```
# HW4 P159, 26, 29, 30, Prob. C, D  
Only plot the sequence of functions $f_n(x)$, not the sum.  

## 29
\[f_n(x)=ne^{-nx}\]
Notice that when $x = 0$, $f_n(x) = n$  
```{r}
f.29 <- function(x,n) n*exp(-n*x)
plot.f(f.29,  N_range =c(1, 2, 3, 4, 5, 20), xaxis_range = c(-5, 5), y2 = 10)
```
  
## 30
\[f_n(x)=\frac{x}{n^{a} (1+nx^{2})}\]  
If a = 0.1   
```{r}
f.30 <- function(x,n,a = 0.1) x/(n^a*(1 + n*x^2))
plot.f(f.30,  N_range =c(1, 2, 3, 4, 5, 100), xaxis_range = c(-5, 5))
```
  
If a = 1   
```{r}
f.30 <- function(x,n,a = 1) x/(n^a*(1 + n*x^2))
plot.f(f.30,  N_range =c(1, 2, 3, 4, 5, 100), xaxis_range = c(-5, 5))
```

## Prob C
\[f_n(x) = \frac{cos[(2n-1)x]}{(2n-1)^{2}}\]
Notice that if $n = 1$, $f_n(x) = cos(x)$  
```{r}
f.probC <- function(x,n) {cos((2*n-1)*x) / (2*n-1)^2}
plot.f(f.probC,  N_range =c(1, 2, 3, 4, 5), xaxis_range = c(-5, 5))
```


# HW3 P149, 9: a, c, d, e, f and Prob.B  
```{r}
# functions for HW3 P147. 9, plot those convergent functions 
f.a <- function(x,n)(x^n)
f.b <- function(x,n)(n^2*x/((1-x^2)^n))
f.c <- function(x,n)(n*x/(1+n*x))
f.d <- function(x,n){n*x/(1+(n*x)^2)}
f.e <- function(x,n){x*exp(-n*x)}
f.f <- function(x,n){n*x*exp(-n*x)}

```

## 9.a  
\[f_n(x)=x^n, x\in(-1,1]\]
```{r}
plot.f(f = f.a, xaxis_range = c(-1,1), N_range = c(1:5, 10,20,100))
```
  
## 9.c  
\[f_n(x)=\frac{nx}{1+nx}, x\in[0, \infty)\]  
```{r}
plot.f(f = f.c)
```
  
## 9.d  
\[f_n(x)=\frac{nx}{1+(nx)^2}, x\in[0, \infty)\]  
```{r}
plot.f(f.d)
```
  
## 9.e  
\[f_n(x)=xe^{-nx}, x\in[0, \infty)\]
```{r}
plot.f(f.e)
```
  
## 9.f  
\[
f_n(x)=nxe^{-nx}, x\in[0, \infty)
\]  
```{r}
plot.f(f.f)
```
  

## Prob. B  
\[
f_n(x) = 
\begin{aligned}
0   && if & x\in [-1,-\frac{1}{n}]\\
\frac{n}{2}x+\frac{1}{2} && if& x\in[-\frac{1}{n},\frac{1}{2}]\\
1 &&if& x\in (\frac{1}{n}, 1]
\end{aligned}\\
\]
```{r}
# HW3. Prob B
x = c(-1,-1/2,1/2,1)
x2 = c(-1,-1/3,1/3,1)
x3 = c(-1,-1/6,1/6,1)
y = c(0,0,1,1)
df <- as.data.frame(cbind(x,x2,x3, y))
# '#DCEDC8','#42B3D5' ,'#1A237E'
ggplot(data=df, aes(x=x,y=y))  + 
  geom_line(lwd = 1, color = '#DCEDC8') + 
  geom_line(data = df, aes(x = x2, y = y), color = '#42B3D5', lwd = 0.7) + 
  geom_line(data = df, aes(x = x3, y = y), color = '#1A237E', lwd = 0.4) + 
  geom_vline(xintercept = 0, color = 'grey') +
  geom_hline(yintercept = 0, color = 'grey') + 
  scale_y_continuous(limits = c(0,1.2)) +
  scale_x_continuous(limits = c(-1.5,1.5), breaks = c(-1,-1/2,1/2,1),labels = c(-1, "-1/n", "1/n", 1))+
  labs(y = 'fn(x)') + 
  theme_classic() 
```

# Code  
This document is reproducible in R using Rmarkdown, code is host on my github: [(here is the link).](https://github.com/liuyanguu/Math/blob/master/Figures%20showing%20function%20convergence.Rmd)   

